The preceeding technique for modeling water infrastructure can accurately rank the social benefit gained by making an intervention, thus allowing decision-making entities (government or NGO) more confident that their decisions are actually providing the maximum assistance possible.
The model is quick and, with further development, simple enough to use.
This ensures faster decision making, and thus more time to implement the intervention, saving more time and lives in water poor areas.

This model has assumptions that could be improved significantly with more data.
Specifically, the spatial data of respondents to the DHS program survey.
The more data that the humanitarian aid and research communities can compile, the stronger, and more efficient optimization techniques like this one will be in assessing where to enact water infrastructure interventions.

In its current form, it is the researchers' opinion that this model would be best implemented as a metaphorical sieve.
It can be used to identify the top several water infrastructure interventions in an area of the country, which then can be further analyzed by experts through field work in order to quickly find the most beneficial intervention.

The AMM research team is also working on a technique to identify the most efficient order in which to enact the water infrastructure changes mentioned here.
Solving this problem would give practitioners a tool to understand the amount of benefit a certain water infrastructure budget would give to citizens.
